Estimating contemporary migration numbers of adults for iteroparous species using kinship pairs found between populations

### 2022-02-02 latex/ms.tex
write 3rd para in Intro, #15

There are essentially two approaches for estimating the contemporary migration rate. The first is to use the mark-recapture (MR) method that directly estimates migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}. The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval. While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and reporting rate (REF). In addition, the MR method for estimating migration rate is generally limited in practice to situations where collection of a sufficient number of adult sample at multiple sites in a short period is available.

@@

@@

There are essentially two approaches for estimating the migrant number. The first is to use the mark-recapture method estimate it directly from the population dynamics modeling with survey data. The second is to ...

>>>>

There are essentially two approaches for estimating the contemporary migration rate. The first is to use the mark-recapture (MR) method that estimates migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}. The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval. While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and reporting rate (REF). In addition, the MR method for estimating migration rate is generally limited in practice to situations where collection of a sufficient number of adult sample at multiple sites in a short period is available.

The second is to use numerous genetic markers to assign individuals to source populations, allowing the inference of recent migration \cite[since][]{Pritchard_2000}. The model of \cite{Wilson_2003}, which is an one of such population assignment (PA) methods, can output point estimates of a current migration matrix. However,

@@

%pop assiginment method だと、mが結構大きい場合は検出されない。Hastingsが言っているような0.1よりも大きい時

@@

The inference model implemented by bayesass assumes linkage equilibrium but allows for deviations from Hardy– Weinberg equilibrium by estimating population-specific inbreeding coefficients. Migration rates among populations can be asymmetric but are constant over short periods of time (two generations). Additionally, it is assumed that migration rates are small (see Appendix A in Wilson  Rannala 2003). These two latter assumptions impose a constraint on the range of migration rates that can be considered by the method. More precisely, the total proportion of migrant individuals into a population per generation cannot exceed 1,3. Thus, nonmigrant proportions must be in the interval 2,3 to 1. The method also assumes that genetic drift and migration during the last few generations do not change subpopulation allele frequencies.
